Capacity and Utilization analysis of Toronto shelter(2024)

### 2024-09-27 paper/paper.qmd
Update and rename paper_Li.qmd to paper.qmd

The project is structure base on Rohan's principes [@rohan], and used the **R** programming language [@citeR], the `tidyverse` [@thereferencecanbewhatever] package were used to simulate the dataset and generate tests for it. The `opendatatoronto` [@citeopendatatoronto] and `tidyverse` [@thereferencecanbewhatever] packages were then applied in order to download the raw Toronto Public shelter dataset. Next, the `tidyverse` package [@thereferencecanbewhatever] was used to clean the raw dataset and test the cleaned dataset.

@@

After loading the dataset using the R programming language [@citeR] and the `here` package [@citehere], the `tidyverse` [@thereferencecanbewhatever] package was used to generate graphs. In doing so, R code was adapted from [@tellingstorieswithdata].

>>>>

The project is structure base on Rohan's principes [@rohan], and used the **R** programming language [@citeR], the `tidyverse` [@citetidyverse] package were used to simulate the dataset and generate tests for it. The `opendatatoronto` [@citeopendatatoronto] and `tidyverse` [@citetidyverse] packages were then applied in order to download the raw Toronto Public shelter dataset. Next, the `tidyverse` package [@citetidyverse] was used to clean the raw dataset and test the cleaned dataset. The `knitr` packages help illustrate the sample data (Xie 2024)

@@

After loading the dataset using the R programming language [@citeR] and the `here` package [@citehere], the `tidyverse` [@citetidyverse] package was used to generate graphs. In doing so, R code was adapted from [@tellingstorieswithdata].
